Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/theory_results.tex

% Theorem 1
\begin{thm}
There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{mult}}$ and $\ep_{\text{bolt}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
\begin{equation}
\forall_{s \in \mathcal{S}_G}: | V_G^{\pi_{GA}}(s) - V_G^{\pi_G^*}(s) | \leq poly(\epsilon).
\end{equation}
\end{thm}

@@

% Possibly a lemma for NP-Completeness of the minimal such phi for all abstractions (was a result for model in previous cases).

% Subsection: Other Abstractions
\subsection{Other Abstractions}

We note that one natural way of approximating $\phi_{a^*}$ from ~\cite{li2006towards}, in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action. A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action. Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.

We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.

Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results. Furthermore, an MDP for which this is true is an awfully weird MDP...

Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.

We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`

>>>>

% Theorem 1
\begin{thm}
There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
\begin{equation}
\forall_{s \in \mathcal{S}_G}: | V_G^{\pi_{GA}}(s) - V_G^{\pi_G^*}(s) | \leq poly(\epsilon).
\end{equation}
\end{thm}
\enote{Axe the absolute values here and elsewhere}

@@

The proof follows a near identical strategy to that of Lemma~\ref{lma:bolt_lemma}.

\dnote{Bounds for multi and bolt suspisiously similar. Double check math}

% Subsection: Other Abstractions
%\subsection{Other Abstractions}
%
%We note that one natural way of approximating $\phi_{a^*}$ from , in which states that are compressed together share optimal actions and the Q values of these actions are within $\varepsilon$ is ultimately equivalent to the crisp abstraction $\phi_{\pi^*}$, in states that are compressed share an optimal action. A true approximation of $\phi_{a^*}$ ought to also approximate the optimality of each action. Given the degree of compression achievable under $\phi_{a^*}$, especially with temporally extended actions, we foresee this approximate form of abstraction as being of great interest, and plan to investigate it in future work.
%
%We are {\it not} going to provide results for $\phi_{\pi^*}$, since relaxing equality of optimal actions doesn't mean anything.
%
%Additionally, we are {\it not} going to provide results for $\phi_{Q^\pi}$, since as Lihong's paper notes, ``It is an open question how to find $Q^\pi$ irrelevance abstractions without enumerating all possible policies, they do not give results. Furthermore, an MDP for which this is true is an awfully weird MDP...
%
%Lastly, we are interested in a generalization of $\phi_{mult}$  and $\phi_{bolt}$ that handles a broader space of distributions over Q values.
%
%We also note that any abstraction that depends only on the reward function, $\mathcal{R}$, can incur unbounded error (or rather, $\textsc{VMax}$).`
